AGB Stars in the IR: Physical Characteristics, Galactic Spatial Distribution, and Chemical Impact of the Milky Way AGB Population

### 2015-07-30 paper1/paper1_data.tex
Updates!

>>>>

\subsection{WISE+2MASS Stellar Locus}
We begin to extract the stellar locus from ALLWISE by centering on the LMC ($276.5^\circ < l < 284^\circ$, $-38.2^\circ < b < -28^\circ$) by necessitating that every object have 1 2MASS association, [$W1/W2/W3$] signal-to-noise $>$ 1, detections in 2MASS J, H, and K,  and confusion \& contamination flags set to 0 for [$W1/W2/W3$]. We then adapt the color-color criteria from \cite{2014MNRAS.440.3430D}. Their locus focuses on stars with effective temperatures $3540 < T_\text{eff} < 7200 K$. We fit their criteria for $J-K_s$ vs $W1 - W2$ within 3$\sigma$ of the locus with degree-3 polynomials. The resulting fit for the 3$\sigma$ stellar locus follows:

\begin{eqnarray}
(J - K_s) & < & 61.67(W1-W2)^3 - 17.88(W1-W2)^2 + 1.68(W1-W2) + 0.99\\
(J - K_s) & > & 40.19(W1-W2)^3 - 9.78(W1-W2)^2 + 0.54(W1-W2) + 0.64
\end{eqnarray}

The resulting locus sample, as well as the original \cite{2014MNRAS.440.3430D} bounds and locus are showin in Fig~\ref{fig:locus}. Note that our sample goes beyond the limits of the stated locus.

\begin{figure}[h]
\includegraphics[width=3in]{figs/lmc_locus_3sig.png}
\caption{The WISE-2MASS stellar locus. \label{fig:locus}}
\end{figure}
